New_Data_Coherence

### 2019-08-25 Analysis/Coherence_Calculations_New.Rmd
change string to links for biogrid

```{r}
# #Reading in biogrid data
# 
# links = read_tsv("./data/BIOGRID-ALL-3.5.174.mitab.txt")
# 
# #Select human protein-protein interactions
# 
# links = links %>% filter(`Taxid Interactor A` == "taxid:9606" & `Taxid Interactor B` == "taxid:9606")
# 
# #Split based on Biogrid ID system then pull out gene names
# 
# protein1 = lapply(strsplit(links$`Alt IDs Interactor A`, "locuslink:"), function(x) strsplit(x[2], "\\|")[[1]][1])
# protein2 = lapply(strsplit(links$`Alt IDs Interactor B`, "locuslink:"), function(x) strsplit(x[2], "\\|")[[1]][1])
# 
# protein1 = unlist(protein1)
# protein2 = unlist(protein2)
# 
# #Place into matrix in form that disease2frame works on
# 
# links = links %>% mutate(protein1 =protein1, 
#                              protein2 = protein2) %>% dplyr::select(protein1, protein2)
# 
# links = links %>% dplyr::select(hgnc_symbol_a = protein1,hgnc_symbol_b = protein2)
# 
# 
# dim(links)
# 
```

@@

```{r}
# msig = readRDS("KEGG_Biogrid.rds")
# msig =msig %>% filter(Category == "CP:KEGG")
# coherence_tab = bind_rows()
# for (i in unique(dis_slopes_biogrid_count$Disease)) {
#   print(i)
#   dis = dis_slopes_biogrid_count %>% filter(Disease == i)
#   msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
#   msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]
#   
#   diseases = bind_rows()
#   j = 1
#     while(j<11) {
#     diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
#     diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
#     if (any(diseases_curr$Internal !=0)) {
#       j = j+1
#       diseases = bind_rows(diseases, diseases_curr)
# 
#     }
#     }
#   
#       mod_rand = lm(External ~ Internal-1, data = diseases)
#       rand_slope = coef(mod_rand)[[1]]
#       
#       coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
#       coherence = data.frame(Disease = dis$Disease, Coherence = coherence, Msig_Norm = median(msigs$Slope, na.rm = TRUE), Rand_Norm = rand_slope )      
#       coherence_tab = bind_rows(coherence, coherence_tab)
#       saveRDS(coherence_tab, "coherence_biogrid.rds")
# }
#   
#   
#
```

@@

```{r}
# msig = readRDS("KEGG_String_Filt.rds")
# msig =msig %>% filter(Category == "CP:REACTOME") %>% filter(!is.na(Slope))
# coherence_tab = bind_rows()
# for (i in unique(dis_slopes_string_filt_count$Disease)) {
#   print(i)
#   dis = dis_slopes_string_filt_count %>% filter(Disease == i)
#   msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
#   msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]
#   
#   diseases = bind_rows()
#   j = 1
#     while(j<11) {
#     diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
#     diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
#     if (any(diseases_curr$Internal !=0)) {
#       j = j+1
#       diseases = bind_rows(diseases, diseases_curr)
# 
#     }
#     }
#   
#       mod_rand = lm(External ~ Internal-1, data = diseases)
#       rand_slope = coef(mod_rand)[[1]]
#       
#       coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
#       coherence = data.frame(Disease = dis$Disease, Coherence = coherence)
#       
#       coherence_tab = bind_rows(coherence, coherence_tab)
#       saveRDS(coherence_tab, "coherence_string_filt_react.rds")
# }
#   
#   
# 
```{r}
# msig = readRDS("KEGG_Biogrid.rds")
# msig =msig %>% filter(Category == "CP:REACTOME") %>% filter(!is.na(Slope))
# coherence_tab = bind_rows()
# for (i in unique(dis_slopes_biogrid_count$Disease)) {
#   print(i)
#   dis = dis_slopes_biogrid_count %>% filter(Disease == i)
#   msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
#   msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]
#   
#   diseases = bind_rows()
#   j = 1
#     while(j<11) {
#     diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
#     diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
#     if (any(diseases_curr$Internal !=0)) {
#       j = j+1
#       diseases = bind_rows(diseases, diseases_curr)
# 
#     }
#     }
#   
#       mod_rand = lm(External ~ Internal-1, data = diseases)
#       rand_slope = coef(mod_rand)[[1]]
#       
#       coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
#       coherence = data.frame(Disease = dis$Disease, Coherence = coherence)
#       
#       coherence_tab = bind_rows(coherence, coherence_tab)
#       saveRDS(coherence_tab, "coherence_biogrid_react.rds")
# }
#   
#   
# ```
# 
# # CC
# 
# ```{r}
# msig = readRDS("KEGG_String.rds")
# msig =msig %>% filter(Category == "CC") %>% filter(!is.na(Slope))
# coherence_tab = bind_rows()
# for (i in unique(dis_slopes_string_count$Disease)) {
#   print(i)
#   dis = dis_slopes_string_count %>% filter(Disease == i)
#   msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
#   msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]
#   
#   diseases = bind_rows()
#   j = 1
#     while(j<11) {
#     diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
#     diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
#     if (any(diseases_curr$Internal !=0)) {
#       j = j+1
#       diseases = bind_rows(diseases, diseases_curr)
# 
#     }
#     }
#   
#       mod_rand = lm(External ~ Internal-1, data = diseases)
#       rand_slope = coef(mod_rand)[[1]]
#       
#       coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
#       coherence = data.frame(Disease = dis$Disease, Coherence = coherence, Msig_Norm = median(msigs$Slope, na.rm = TRUE), Rand_Norm = rand_slope )
#       
#       coherence_tab = bind_rows(coherence, coherence_tab)
#       saveRDS(coherence_tab, "coherence_string_CC.rds")
# }
#   
# 
# ```
# 
# ```{r}
# msig = readRDS("KEGG_String_Filt.rds")
# msig =msig %>% filter(Category == "CC") %>% filter(!is.na(Slope))
# coherence_tab = bind_rows()
# for (i in unique(dis_slopes_string_filt_count$Disease)) {
#   print(i)
#   dis = dis_slopes_string_filt_count %>% filter(Disease == i)
#   msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
#   msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]
#   
#   diseases = bind_rows()
#   j = 1
#     while(j<11) {
#     diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
#     diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
#     if (any(diseases_curr$Internal !=0)) {
#       j = j+1
#       diseases = bind_rows(diseases, diseases_curr)
# 
#     }
#     }
#   
#       mod_rand = lm(External ~ Internal-1, data = diseases)
#       rand_slope = coef(mod_rand)[[1]]
#       
#       coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
#       coherence = data.frame(Disease = dis$Disease, Coherence = coherence)
#       
#       coherence_tab = bind_rows(coherence, coherence_tab)
#       saveRDS(coherence_tab, "coherence_string_filt_CC.rds")
# }
#   
#   
# ```
# 
# ```{r}
# msig = readRDS("KEGG_Biogrid.rds")
# msig =msig %>% filter(Category == "CC") %>% filter(!is.na(Slope))
# coherence_tab = bind_rows()
# for (i in unique(dis_slopes_biogrid_count$Disease)) {
#   print(i)
#   dis = dis_slopes_biogrid_count %>% filter(Disease == i)
#   msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
#   msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]
#   
#   diseases = bind_rows()
#   j = 1
#     while(j<11) {
#     diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
#     diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
#     if (any(diseases_curr$Internal !=0)) {
#       j = j+1
#       diseases = bind_rows(diseases, diseases_curr)
# 
#     }
#     }
#   
#       mod_rand = lm(External ~ Internal-1, data = diseases)
#       rand_slope = coef(mod_rand)[[1]]
#       
#       coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
#       coherence = data.frame(Disease = dis$Disease, Coherence = coherence)
#       
#       coherence_tab = bind_rows(coherence, coherence_tab)
#       saveRDS(coherence_tab, "coherence_biogrid_CC.rds")
# }
#   
#   
# 

>>>>

```{r}
# #Reading in biogrid data
# 
# links = read_tsv("./data/BIOGRID-ALL-3.5.174.mitab.txt")
# 
# #Select human protein-protein interactions
# 
# links = links %>% filter(`Taxid Interactor A` == "taxid:9606" & `Taxid Interactor B` == "taxid:9606")
# 
# #Split based on Biogrid ID system then pull out gene names
# 
# protein1 = lapply(strsplit(links$`Alt IDs Interactor A`, "locuslink:"), function(x) strsplit(x[2], "\\|")[[1]][1])
# protein2 = lapply(strsplit(links$`Alt IDs Interactor B`, "locuslink:"), function(x) strsplit(x[2], "\\|")[[1]][1])
# 
# protein1 = unlist(protein1)
# protein2 = unlist(protein2)
# 
# #Place into matrix in form that disease2frame works on
# 
# links = links %>% mutate(protein1 =protein1,
#                              protein2 = protein2) %>% dplyr::select(protein1, protein2)
# 
# links = links %>% dplyr::select(hgnc_symbol_a = protein1,hgnc_symbol_b = protein2)
# 
# 
# dim(links)

@@

```{r}
# msig = readRDS("KEGG_Biogrid.rds")
# msig =msig %>% filter(Category == "CP:KEGG")
# coherence_tab = bind_rows()
# for (i in unique(dis_slopes_biogrid_count$Disease)) {
#   print(i)
#   dis = dis_slopes_biogrid_count %>% filter(Disease == i)
#   msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
#   msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]
# 
#   diseases = bind_rows()
#   j = 1
#     while(j<11) {
#     diseases_curr = GeneSample(dis$Count, links, directed = FALSE)
#     diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
#     if (any(diseases_curr$Internal !=0)) {
#       j = j+1
#       diseases = bind_rows(diseases, diseases_curr)
# 
#     }
#     }
# 
#       mod_rand = lm(External ~ Internal-1, data = diseases)
#       rand_slope = coef(mod_rand)[[1]]
# 
#       coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
#       coherence = data.frame(Disease = dis$Disease, Coherence = coherence, Msig_Norm = median(msigs$Slope, na.rm = TRUE), Rand_Norm = rand_slope )
#       coherence_tab = bind_rows(coherence, coherence_tab)
#       print(coherence_tab)
#       saveRDS(coherence_tab, "coherence_biogrid.rds")
# }

@@

```{r}
# msig = readRDS("KEGG_String_Filt.rds")
# msig =msig %>% filter(Category == "CP:REACTOME") %>% filter(!is.na(Slope))
# coherence_tab = bind_rows()
# for (i in unique(dis_slopes_string_filt_count$Disease)) {
#   print(i)
#   dis = dis_slopes_string_filt_count %>% filter(Disease == i)
#   msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
#   msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]
#   
#   diseases = bind_rows()
#   j = 1
#     while(j<11) {
#     diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
#     diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
#     if (any(diseases_curr$Internal !=0)) {
#       j = j+1
#       diseases = bind_rows(diseases, diseases_curr)
# 
#     }
#     }
#   
#       mod_rand = lm(External ~ Internal-1, data = diseases)
#       rand_slope = coef(mod_rand)[[1]]
#       
#       coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
#       coherence = data.frame(Disease = dis$Disease, Coherence = coherence)
#       
#       coherence_tab = bind_rows(coherence, coherence_tab)
#       saveRDS(coherence_tab, "coherence_string_filt_react.rds")
# }
#   
#   
# 
```

```{r}
# msig = readRDS("KEGG_Biogrid.rds")
# msig =msig %>% filter(Category == "CP:REACTOME") %>% filter(!is.na(Slope))
# coherence_tab = bind_rows()
# for (i in unique(dis_slopes_biogrid_count$Disease)) {
#   print(i)
#   dis = dis_slopes_biogrid_count %>% filter(Disease == i)
#   msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
#   msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]
# 
#   diseases = bind_rows()
#   j = 1
#     while(j<11) {
#     diseases_curr = GeneSample(dis$Count, links, directed = FALSE)
#     diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
#     if (any(diseases_curr$Internal !=0)) {
#       j = j+1
#       diseases = bind_rows(diseases, diseases_curr)
# 
#     }
#     }
# 
#       mod_rand = lm(External ~ Internal-1, data = diseases)
#       rand_slope = coef(mod_rand)[[1]]
# 
#       coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
#       coherence = data.frame(Disease = dis$Disease, Coherence = coherence)
# 
#       coherence_tab = bind_rows(coherence, coherence_tab)
#       saveRDS(coherence_tab, "coherence_biogrid_react.rds")
# }
# 
# 
```

# CC

```{r}
# msig = readRDS("KEGG_String.rds")
# msig =msig %>% filter(Category == "CC") %>% filter(!is.na(Slope))
# coherence_tab = bind_rows()
# for (i in unique(dis_slopes_string_count$Disease)) {
#   print(i)
#   dis = dis_slopes_string_count %>% filter(Disease == i)
#   msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
#   msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]
#   
#   diseases = bind_rows()
#   j = 1
#     while(j<11) {
#     diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
#     diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
#     if (any(diseases_curr$Internal !=0)) {
#       j = j+1
#       diseases = bind_rows(diseases, diseases_curr)
# 
#     }
#     }
#   
#       mod_rand = lm(External ~ Internal-1, data = diseases)
#       rand_slope = coef(mod_rand)[[1]]
#       
#       coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
#       coherence = data.frame(Disease = dis$Disease, Coherence = coherence, Msig_Norm = median(msigs$Slope, na.rm = TRUE), Rand_Norm = rand_slope )
#       
#       coherence_tab = bind_rows(coherence, coherence_tab)
#       saveRDS(coherence_tab, "coherence_string_CC.rds")
# }
#   
# 
# ```
# 
# ```{r}
# msig = readRDS("KEGG_String_Filt.rds")
# msig =msig %>% filter(Category == "CC") %>% filter(!is.na(Slope))
# coherence_tab = bind_rows()
# for (i in unique(dis_slopes_string_filt_count$Disease)) {
#   print(i)
#   dis = dis_slopes_string_filt_count %>% filter(Disease == i)
#   msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
#   msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]
#   
#   diseases = bind_rows()
#   j = 1
#     while(j<11) {
#     diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
#     diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
#     if (any(diseases_curr$Internal !=0)) {
#       j = j+1
#       diseases = bind_rows(diseases, diseases_curr)
# 
#     }
#     }
#   
#       mod_rand = lm(External ~ Internal-1, data = diseases)
#       rand_slope = coef(mod_rand)[[1]]
#       
#       coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
#       coherence = data.frame(Disease = dis$Disease, Coherence = coherence)
#       
#       coherence_tab = bind_rows(coherence, coherence_tab)
#       saveRDS(coherence_tab, "coherence_string_filt_CC.rds")
# }
#   
#   
```

```{r}
# msig = readRDS("KEGG_Biogrid.rds")
# msig =msig %>% filter(Category == "CC") %>% filter(!is.na(Slope))
# coherence_tab = bind_rows()
# for (i in unique(dis_slopes_biogrid_count$Disease)) {
#   print(i)
#   dis = dis_slopes_biogrid_count %>% filter(Disease == i)
#   msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
#   msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]
# 
#   diseases = bind_rows()
#   j = 1
#     while(j<11) {
#     diseases_curr = GeneSample(dis$Count, links, directed = FALSE)
#     diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
#     if (any(diseases_curr$Internal !=0)) {
#       j = j+1
#       diseases = bind_rows(diseases, diseases_curr)
# 
#     }
#     }
# 
#       mod_rand = lm(External ~ Internal-1, data = diseases)
#       rand_slope = coef(mod_rand)[[1]]
# 
#       coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
#       coherence = data.frame(Disease = dis$Disease, Coherence = coherence)
# 
#       coherence_tab = bind_rows(coherence, coherence_tab)
#       saveRDS(coherence_tab, "coherence_biogrid_CC.rds")
# }
```
